\subsection{Thesis focus}

\begin{frame}{Thesis focus}
    \begin{itemize}
        \item Accuracy of matrix completion-based methods (WSDM'17$^*$).
        \item Modeling user preferences over sets of items (eKNOW'17, TiiS'17$^*$).
        \item Bilinear models for cold-start item recommendations (SDM'15).
    \end{itemize}
\end{frame}

\begin{frame}{Publications}
    \begin{itemize}
        \item Related to thesis
            \begin{itemize}
                \item Mohit Sharma, Max Harper, and George Karypis. Learning from sets of items in
                  Recommender Systems (eKNOW'17, TiiS'17$^*$).
                \item Mohit Sharma and George Karypis. \TMF: Improving recommendations for the tail (WSDM'17$^*$).
                \item Mohit Sharma, Jiayu Zhou, Junling Hu, and George Karypis.
                  Feature-based factorized Bilinear Similarity Model for Cold-Start \TOPN
                  Item Recommendation. SIAM International Conference on Data Mining (SDM), 2015.
            \end{itemize}
        \item Other
        \begin{itemize}
            \item David C. Anastasiu, Evangelia Christakopoulou, Shaden Smith, Mohit
              Sharma, and George Karypis. Big Data and Recommender Systems. Big Data
              Novatica Special Issue, 2016.
            \item Vishwanathan N., Bandyopadhyay A. Fu H. Sharma M., Johnson K.,
              Mudge J. Ramaraj T., Onsongo G., Silverstein K., Jacob N., Le H.,
              Karypis G., and Hu W. Augmenting Chinese hamster genome assembly by identifying regions
              of high confidence, Biotechnology Journal, 2016.
        \end{itemize}
    \end{itemize}
\end{frame}




